\documentclass[letterpaper,8.7pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{xcolor}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.55in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\normalsize\bfseries
}{}{0em}{}[\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    \begin{tabular*}{0.97\textwidth}{l}
      #1 \vspace{-2pt}
    \end{tabular*}
  }
}

\newcommand{\resumeProjectHeading}[3]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\footnotesize #2} \\
      \textit{\footnotesize #3} & \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.1in]\setlength\itemsep{-1pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\footnotesize #2} \\
      \textit{\footnotesize #3} & \textit{\footnotesize #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\skillCategory}[2]{
  \textbf{#1:} \footnotesize{#2}
}

\newcommand{\contactItem}[2]{
  \footnotesize{#1 #2}
}

\definecolor{LinkBlue}{RGB}{0,102,204}

\begin{document}

\setlength{\parskip}{0pt}
\setlength{\itemsep}{-2pt}
\setlength{\parsep}{0pt}
\linespread{0.97}

%----------HEADER----------
\begin{center}
  {\Huge \scshape Rhythem Sabharwal} \\ \vspace{1pt}
  New Delhi – 110027 \\ \vspace{1pt}
  \href{mailto:rhythemsabharwal@gmail.com}{rhythemsabharwal@gmail.com} ~|~ +91-9599655016 ~|~ 
  \href{www.linkedin.com/in/rhythem-sabharwal-a9027529b}{linkedin.com/in/rhythemsabharwal} ~|~ 
  \href{https://github.com/rhythemsabharwal}{github.com/rhythemsabharwal} ~|~ 
  \href{https://portfolio-pqfa.vercel.app/}{portfolio-pqfa.vercel.app}
\end{center}

\vspace{-12pt}
\section*{About}
Full Stack Developer with a strong foundation in the MERN stack and a focused interest in integrating artificial intelligence into real-world applications. Experienced in architecting scalable systems, developing intelligent web platforms, and continuously strengthening technical expertise through project-driven learning.

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
\item{
    \begin{tabular*}{0.97\textwidth}{l}
        \skillCategory{Programming Languages}{C++, Python} \\[0pt]
        \skillCategory{Frontend Technologies}{React.js, HTML, Tailwind CSS, JavaScript} \\[0pt]
        \skillCategory{Backend Technologies}{Node.js, Express.js, Flask, RESTful APIs} \\[0pt]
        \skillCategory{Databases}{MongoDB, SQL} \\[0pt]
        \skillCategory{Tools \& Platforms}{Git, GitHub, Postman, Vercel, Render, VS Code} \\[0pt]
    \end{tabular*}
}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {FarmWise - AI-Powered Farmer Support Platform (Team Project)}{Aug 2025 -- Nov 2025}
    {React.js, Flask, OpenCV, XGBoost, Weather API, JWT Authentication, Tailwind CSS}
  \resumeItemListStart
    \resumeItem{Developed an AI-driven crop diagnosis and recommendation system leveraging XGBoost and OpenCV for accurate image-based disease detection.}
    \resumeItem{Integrated Weather API services to provide automated climate insights and implemented JWT-based authentication to ensure secure access for farmers and experts.}
    \resumeItem{Implemented chatbot assistance and a fully responsive React and Tailwind CSS frontend to enhance user engagement and usability.}
    \resumeItem{Defined a future roadmap encompassing IVR support, SIM-based location retrieval, and integration with government APIs.}
  \resumeItemListEnd

  \resumeProjectHeading
    {AI Image Generator - Full-Stack Platform \href{https://artbot-frontend.onrender.com/}{\textcolor{LinkBlue}{\faLink}}}{June 2025}
    {MongoDB, Express.js, React.js, Node.js, ClipDrop API, Tailwind CSS, JWT}
  \resumeItemListStart
    \resumeItem{Developed a full-stack web application that converts text prompts into high-quality AI-generated images using the ClipDrop API.}
    \resumeItem{Implemented secure authentication using JWT and bcrypt to manage user accounts and session handling.}
    \resumeItem{Gained advanced experience in prompt engineering, API integration, and asynchronous image generation workflows.}
    \resumeItem{Deployed the frontend on Vercel and the backend on Render to enable scalable and reliable hosting.}
  \resumeItemListEnd

  \resumeProjectHeading
    {Amrutum - Prompt Engineered AI Project \href{https://amrutam-xi.vercel.app/}{\textcolor{LinkBlue}{\faLink}}}{Apr 2024}
    {Prompt Engineering, Tailwind CSS, React.js}
  \resumeItemListStart
    \resumeItem{Developed a prompt-engineered web application using Tailwind CSS for a hospital management system to analyze real-world AI use cases.}
    \resumeItem{Designed as part of an internship selection process to demonstrate proficiency in prompt engineering, frontend development, and AI system design.}
    \resumeItem{Explored context-aware prompt optimization and built an interactive React interface for effective AI response visualization.}
  \resumeItemListEnd

  \resumeProjectHeading
    {AI Code Reviewer}{April 2025}
    {EJS, Node.js, Google Gemini API}
  \resumeItemListStart
    \resumeItem{Developed an automated AI-based code review tool utilizing the Google Gemini API to deliver intelligent and actionable feedback.}
    \resumeItem{Implemented a responsive frontend featuring syntax highlighting and real-time code evaluation metrics.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Minor in Artificial Intelligence} — \textit{IIT Ropar}}{Aug 2024  (Ongoing)}{\vspace{-8pt}}
  \resumeItemListStart
    \resumeItem{Key topics covered include Data Handling, Introduction to Prompt Programming, CNNs, Neural Links and Advanced LLMs, Computer Vision, and Natural Language Processing.}
    \resumeItem{Specialization in \textbf{TinyML and General Applications in Artificial Intelligence}.}
   
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Mastering DSA in C++} — \textit{Coding Blocks}}{May 2025 – Dec 2025 }{\vspace{-8pt}}
  \resumeItemListStart
    \resumeItem{Completed a comprehensive  program focused on Data Structures, Algorithms, and advanced problem-solving techniques in C++.}
    \resumeItem{Covered core concepts including recursion, sorting, searching, stacks, queues, trees, graphs, dynamic programming, tries, greedy algorithms, and backtracking.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

  \resumeSubheading
    {Bhagwan Parshuram Institute Of Technology}{New Delhi, India}
    {Bachelor of Technology in Computer Science and Engineering (CGPA: 7.3)}{Aug 2023 -- Aug 2027}

  \resumeSubheading
    {Indian Institute Of Technology, Ropar}{Punjab, India}
    {Minor in Artificial Intelligence }{Aug 2024 -- Ongoing}

  \resumeSubheading
    {G.D. Goenka Public School, Paschim Vihar}{New Delhi, India}
    {Class 12\textsuperscript{th} — Percentage: 65\%}{2023}

  \resumeSubheading
    {G.D. Goenka Public School, Paschim Vihar}{New Delhi, India}
    {Class 10\textsuperscript{th} — Percentage: 75\%}{2021}

\resumeSubHeadingListEnd

\end{document}
